Universal Anonymous Signatures

### 2022-10-06 prism-backend/research/gsac/formal-uas.tex
Some rewriting..

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue (see \figref{fig:exp-uas-unfor}). It captures that all honestly
issued credentials meet the requirements set by the corresponding issuer, and
that any further credential
involved in the request is a valid credential, bound to the same known user. For
this, we allow the adversary \adv~to interact with the oracles (restricted to
honest issuers). Eventually, \adv~is challenged to output a credential \Cred
from which we extract the actual witnesses used in the credential request
associated to \cid. \adv~wins if the issuance function, applied to the extracted
values, does not meet the expected output, if not all of the credentials (if
any) used to endorse the request belong to the same (known) user to whom the new
credential was issued, or if any of such credentials is a forgery. Note that the
issuance transcript associated to the credential output by the adversary must
exist, as we unavoidably need to restrict to honest issuers. Indeed, a dishonest
issuer cannot be trusted to enforce any policy, nor to properly keep all
transcripts.

>>>>

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue (see \figref{fig:exp-uas-unfor}). It captures that all honestly
issued credentials meet the requirements set by the corresponding issuer, and
that any further credential
involved in the request is a valid credential, bound to the same known user. For
this, we allow the adversary \adv~to interact with the oracles (restricted to
honest issuers). Eventually, \adv~is challenged to output a credential
$\Cred=(\cid,\attrs,\cred,\ipk)$. Using \cid, we extract the actual witnesses
used in the credential request $\utrans[\cid]$. \adv~wins if the issuance
function, applied to the extracted
values, does not meet the expected output, if not all of the credentials (if
any) used to endorse the request belong to the same (known) user to whom the new
credential was issued, or if any of such credentials is not a valid signature by
its issuer, or it is, but is a forgery. Note that the
issuance transcript associated to the credential output by the adversary must
exist, as we unavoidably need to restrict to honest issuers. Indeed, a dishonest
issuer cannot be trusted to enforce any policy, nor to properly keep all
transcripts.
